---
title:  "Activity: Street or Road?"
author: "Dave Friedman"
date:   "20 Jun 2023"
output: html_notebook
---

## Load in the data

```{r}
library(lubridate)
library(rvest)
library(tidyverse)

str_c('EXECUTED : ', now())
sessionInfo()

# about 15,000 street addresses of registered voters in Wake County, NC
Addresses <- read_csv('https://mdbeckman.github.io/dcSupplement/data/street-addresses.csv')
head(Addresses)
```

## Recreate Solved Example using `sample(50)`

```{r}
Sample <-
  Addresses %>%
    sample_n(size = 50)
head(Sample)

pattern <- 'PO'

Matches <-
  Sample %>%
    filter(grepl(pattern = pattern, address))
head(Matches)

Dont <-
  Sample %>%
    filter(!grepl(pattern = 'PO', address))
head(Dont)

pattern <- 'BOX\\s+(\\d+)'

Matches <-
  Sample %>%
    filter( grepl(pattern, address))
head(Matches)

Dont <-
  Sample %>%
    filter(!grepl(pattern, address))
head(Dont)

BoxNumbers <-
  Sample %>%
    filter(grepl(pattern, address)) %>%
    tidyr::extract(address, into = 'boxnum', regex = pattern)
head(BoxNumbers)
```

## Recreate Soved Example using the entire `Address` data set

```{r}
pattern <- 'PO'

Matches <-
  Addresses %>%
    filter(grepl(pattern = pattern, address))
head(Matches)

Dont <-
  Addresses %>%
    filter(!grepl(pattern = 'PO', address))
head(Dont)

pattern <- 'BOX\\s+(\\d+)'

Matches <-
  Addresses %>%
    filter( grepl(pattern, address))
head(Matches)

Dont <-
  Addresses %>%
    filter(!grepl(pattern, address))
head(Dont)

BoxNumbers <-
  Addresses %>%
    filter(grepl(pattern, address)) %>%
    tidyr::extract(address, into = 'boxnum', regex = pattern)
head(BoxNumbers)
```

#### Additional Question: How many addresses are a PO BOX (including NCSU BOX)? 

$11,100$ addresses are a PO BOX (including NCSU BOX).

```{r}
Addresses %>%
  filter(grepl(pattern, address))
```

## Back to the Streets: Your Turn

#### Part 1: Explain (in english) each line of the following code chunk

```{r}
pattern <- '(ST|RD|ROAD)'

LeftOvers <-
  Addresses %>%
    filter(
      !grepl(pattern, address),                 # matches other than: 'ST' or 'RD' or 'ROAD'
      !grepl('\\sAPT|UNIT\\s[\\d]+$', address), # matches other than: (1 whitespace, 'APT') or ('UNIT', 1 whitespace, 1 or more digits at the end of the string)
      !grepl(' BOX ', address)                  # matches other than: 1 space, 'BOX', 1 space
    )
```

#### Part 2: Implement your method on the entire `Addresses` data set. Explain how your code works line by line.

```{r}
Addresses %>%
  filter(
    !grepl(pattern = ' AVENUE |AVENUE$', x = address),       # matches other than: 'AVENUE' flanked by whitespace anywhere in the string, or 'AVENUE' at the end of the string
    !grepl(pattern = ' AVE |AVE$', x = address),             # matches other than: 'AVE' flanked by whitespace anywhere in the string, or 'AVE' at the end of the string
    !grepl(pattern = ' BLVD |BLVD$', x = address),           # matches other than: 'BLVD' flanked by whitespace anywhere in the string, or 'BLVD' at the end of the string
    !grepl(pattern = ' BOULEVARD |BOULEVARD$', x = address), # matches other than: 'BOULEVARD' flanked by whitespace anywhere in the string, or 'BOULEVARD' at the end of the string
    !grepl(pattern = ' CIR |CIR$', x = address),             # matches other than: 'CIR' flanked by whitespace anywhere in the string, or 'CIR' at the end of the string
    !grepl(pattern = ' CIRCLE |CIRCLE$', x = address),       # matches other than: 'CIRCLE' flanked by whitespace anywhere in the string, or 'CIRCLE' at the end of the string
    !grepl(pattern = ' CT |CT$', x = address),               # matches other than: 'CT' flanked by whitespace anywhere in the string, or 'CT' at the end of the string
    !grepl(pattern = ' COURT |COURT$', x = address),         # matches other than: 'COURT' flanked by whitespace anywhere in the string, or 'COURT' at the end of the string
    !grepl(pattern = ' DR |DR$', x = address),               # matches other than: 'DR' flanked by whitespace anywhere in the string, or 'DR' at the end of the string
    !grepl(pattern = ' DRIVE |DRIVE$', x = address),         # matches other than: 'DRIVE' flanked by whitespace anywhere in the string, or 'DRIVE' at the end of the string
    !grepl(pattern = ' LN |LN$', x = address),               # matches other than: 'LN' flanked by whitespace anywhere in the string, or 'LN' at the end of the string
    !grepl(pattern = ' LANE |LANE$', x = address),           # matches other than: 'LANE' flanked by whitespace anywhere in the string, or 'LANE' at the end of the string
    !grepl(pattern = ' PL |PL$', x = address),               # matches other than: 'PL' flanked by whitespace anywhere in the string, or 'PL' at the end of the string
    !grepl(pattern = ' PLACE |PLACE$', x = address),         # matches other than: 'PLACE' flanked by whitespace anywhere in the string, or 'PLACE' at the end of the string
    !grepl(pattern = ' RD |RD$', x = address),               # matches other than: 'RD' flanked by whitespace anywhere in the string, or 'RD' at the end of the string
    !grepl(pattern = ' ROAD |ROAD$', x = address),           # matches other than: 'ROAD' flanked by whitespace anywhere in the string, or 'ROAD' at the end of the string
    !grepl(pattern = ' ST |ST$', x = address),               # matches other than: 'ST' flanked by whitespace anywhere in the string, or 'ST' at the end of the string
    !grepl(pattern = ' STREET |STREET$', x = address),       # matches other than: 'STREET' flanked by whitespace anywhere in the string, or 'STREET' at the end of the string
    !grepl(pattern = ' TRAIL |TRAIL$', x = address),         # matches other than: 'TRAIL' flanked by whitespace anywhere in the string, or 'TRAIL' at the end of the string
    !grepl(pattern = ' WAY |WAY$', x = address),             # matches other than: 'WAY' flanked by whitespace anywhere in the string, or 'WAY' at the end of the string
    !grepl(pattern = ' WINERY |WINERY$', x = address),       # matches other than: 'WINERY' flanked by whitespace anywhere in the string, or 'WINERY' at the end of the string
    !grepl(pattern = 'BOX\\s+(\\d+)', x = address)           # filters out all the 'BOX' from above
  )
```

#### Additional Question 1: Present your result from part 2 by providing a table in descending order of popularity for the street name endings you found

```{r}


```

#### Additional Question 2: Present your result by using ggplot to a bar chart in descending order of popularity for the street name endings you found previously.

Note: make sure your order street names according to popularity, not alphabetically.

```{r}

```

#### Additional Question 3: Comment on any patterns you see

My answer here.......